Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-28 paper/ms.tex
working on the correlation function section

We calculate the mean angular correlation function (ACF) only for the
models that showed that all of the 15 mock surveys are consistent
at the $P>0.05$ level with observations. The ACF is computed only the
denseset subfield in all the 15 mock surveys corresponding to the
SSA22 region. These results are compared against the observations
reported by Hayashino et al in 2004 over the same region, which were
also performed on the densest field.

The comparison between the simulated and observed ACFs is also done using a
$R^2$ statistic which includes the information on measurement uncertainties

\begin{equation}
R^{2} = \sum_{\theta_i} \frac{(\xi_{\rm obs}(\theta_i) - \xi_{\rm
    sim}(\theta_i))^2}{\sigma_{\rm obs}^2(\theta_i) + \sigma_{\rm
    sim}^2({\theta_i})}, 
\end{equation}

where the sum is done over all the angle values $\theta_i$ where the
ACF has been computed. In Figure XX we plot the integrated
distributions for this $R^{2}$ statistics

Given that the ACF reported by Hayashino et al en 2004 is taken over
the densest  field oserved in the SSA22 region by  Yamada et el in
2012 it is expected that the predicted ACF in the SSA22 region should
reproduce this observation. In the  left panel of figure
\ref{figure:correlation_match} we can see the predicted ACFs  an their
corresponding standard deviation over the seven fields that mock the
SSA22  region. It can be seen that the model with $M_min=10.6$ seems
to better reproduce the  Hayashino's ACF and that the corresponding
field is in fact an overdense field in the SSA22 region covered by
Yamada et al.

From these tests we conclude that the ACF on small fields does not
provide additional constraints to further select models for halos
hosting LAEs. The reason is that cosmic variance is large and the
statistical uncertainties on the ACF render almost any model
compatible with the observational constraints.

@@

We also present the results for the angular correlation function in
therms of the correlation lenght obtained by fitting the following
function

\begin{equation}
\xi(r) = \left(\frac{r}{r_{0}}\right)^{-\gamma}
\end{equation}

@@

>>>>

we calculate the angular correlation function
(ACF) for all the models having the $15$ mock surveys consistent with
observations. We perform this calculation as a sanity check and
potential additional constraint. The ACF is computed only the densest
subfield in all the 15 mock surveys corresponding to the SSA22
region. These results are compared against the observations reported
by \citep{Hayashino2004} which were also performed on the densest
field of SSA22.

It is important to keep in mind that there are some differences
between this work and \citep{Yamada2012}. The color selection by
\cite{Yamada2012} is less stringent compared to the one by
\cite{Hayashino2004}. Also the EW threshold is different,
\cite{Hayashino2004} uses a cut around $154$\AA instead of $190$\AA
used by \citep{Yamada2012}

The comparison between the simulated and observed ACFs is also done using a
$\chi^2$ statistic which includes the information on the measurement
uncertainties and the statistical dispersio from the $15$ mock surveys
in the simulation

\begin{equation}
\chi^{2} = \sum_{\theta_i} \frac{(\xi_{\rm obs}(\theta_i) - \xi_{\rm
    sim}(\theta_i))^2}{\sigma_{\rm obs}^2(\theta_i) + \sigma_{\rm
    sim}^2({\theta_i})}, 
\end{equation}

where the sum is done over all the $13$ angle values $\theta_i$ where the
ACF has been computed. In Figure XX we plot this statistic for all the
models considered. In all cases $\chi^{2}<7$ which is not sufficient
to consider that the correlation functions from the simulations are
statistically different from the observational one. The constribution
of cosmic variance in the simulations together with the statistical
uncertainties make all tested models compatible with the observational
constraints.

%From these tests we conclude that the ACF on small fields does not
%provide additional constraints to further select models for halos
%hosting LAEs. The reason is that

@@

%Given that the ACF reported by Hayashino et al en 2004 is taken over
%the densest  field oserved in the SSA22 region by  Yamada et el in
%2012 it is expected that the predicted ACF in the SSA22 region should
%reproduce this observation. In the  left panel of figure
%\ref{figure:correlation_match} we can see the predicted ACFs  an their
%corresponding standard deviation over the seven fields that mock the
%SSA22  region. It can be seen that the model with $M_min=10.6$ seems
%to better reproduce the  Hayashino's ACF and that the corresponding
%field is in fact an overdense field in the SSA22 region covered by
%Yamada et al.

We also present the results for the angular correlation function in
therms of the correlation lenght obtained by fitting the following
function
\begin{equation}
\xi(r) = \left(\frac{r}{r_{0}}\right)^{-\gamma}
\end{equation}

@@

%We calculate the mean angular correlation function (ACF) only for the
%models that showed that all of the 15 mock surveys are consistent
%at the $P>0.05$ level with observations.
